Machine Learning Working Notes

### 2016-03-19 ml_notes/draft.tex
update ml_notes

% Employ the following version of the ``usepackage'' statement for
% submitting the draft version of the paper for review.  This will set
% the note in the first column to ``Under review.  Do not distribute.''
\usepackage{icml2016}

% Employ this version of the ``usepackage'' statement after the paper has
% been accepted, when creating the final version.  This will set the
% note in the first column to ``Proceedings of the...''
%\usepackage[accepted]{icml2016}

%-------------------------------------------------------------
%                      Own Commands
%-------------------------------------------------------------
\usepackage{amsmath}
\newcommand{\cbn}{\textsc{Cbn}}
\newcommand{\bn}{\textsc{Bn}}

\renewcommand{\algorithmiccomment}[1]{/* #1 */}
\def\ci{\perp\!\!\!\perp}
\def\dep{\perp\!\!\!\perp\!\!\!\!\!\!\!/\,\,\,\,}
% Theorem & Co environments and counters
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{equat}[theorem]{Equation}
\newtheorem{example}[theorem]{Example}
%-------------------------------------------------------------
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\etal}{\emph{et al.}}
\newcommand{\etc}{\emph{etc.}}
\newcommand{\cf}{\emph{cf.}}
\newcommand{\diff}[2]{\frac{\partial #1}{\partial #2}}
%\newcommand{\diff}[2]{\nabla_{#2}{#1}}
\newcommand{\vct}[1]{\ensuremath{\boldsymbol{#1}}} %for greek letters
\newcommand{\mat}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\set}[1]{\ensuremath{\mathcal{#1}}}
\newcommand{\con}[1]{\ensuremath{\mathsf{#1}}}
\newcommand{\T}{\ensuremath{\top}}
\newcommand{\mycomment}[1]{\textcolor{red}{#1}}
\newcommand{\ind}[1]{\ensuremath{\mathbbm 1_{#1}}}
\newcommand{\argmax}{\operatornamewithlimits{\arg\,\max}}
\newcommand{\erf}{\text{erf}}
\newcommand{\argmin}{\operatornamewithlimits{\arg\,\min}}
\newcommand{\bmat}[1]{\begin{bmatrix}#1\end{bmatrix}}
\newcommand{\mname}{\texttt{OLCS}}

@@

Give a training dataset $\set D = \left\{x_i\right\}_{i=1}^n$ with $x_i \in R^d$, \textit{i.i.d} drawn from certain distribution, we are interested at the predictive distribution of unknown target for the  test sample $x_*$, denoted as $f_*$. Suppose a prior over $\vct y$ given input $\vct X$ is a $n$-variable Gaussian distribution, 
\[
\vct y \sim \set N(\vct 0, K(\vct X, \vct X)) 
\]
where $K(\vct X, \vct X)$ defines a covariance function over $\vct X$. Therefore the posterior of $f_*$ given the training dataset $\set D$ is also a Gaussian. 
\[
f_*|\vct y, \vct X, x_* \sim \set N(\mu_*, \Sigma_*^{-1})
\]
where the sufficient statistics can be derived using Bayesian theorem, 
\begin{align}
	& \mu_* = K_{X_*,X}\left[K_{X,X}+\sigma_n^2 I\right]^{-1}\vct y \label{eq:gpr_mu}\\
	& \Sigma_*^{-1} = K_{X_*,X_*} - K_{X_*,X}\left[K_{X,X}+\sigma_n^2 I\right]^{-1}K_{X,X_*} \label{eq:gpr_cov}
\end{align}
where $\sigma_n^2$ is the noise level and $K_{\cdot,\cdot}$ represents a shorthand for covariance matrix.

To obtain the Eq.\eqref{eq:gpr_mu}-\eqref{eq:gpr_cov}, we can use the following trick. 
Given two variables $(\vct x, \vct y)$ following a Gaussian distribution,
\[
\bmat{\vct x\\ \vct y} \sim \set N\left( 
\bmat{\mu_x \\ \mu_y}, \bmat{A & C \\ C^T & B}
\right)
\]
Then we have the conditional distribution,
\[
\vct x|\vct y \sim \set N\left(\mu_x+CB^{-1}(\vct y - \mu_y), A - C^TB^{-1}C \right)
\]
\bibliography{myrefs}
\bibliographystyle{icml2016}

>>>>

% Employ the following version of the ``usepackage'' statement for
% submitting the draft version of the paper for review.  This will set
% the note in the first column to ``Under review.  Do not distribute.''
\usepackage[accepted]{icml2016}

% Employ this version of the ``usepackage'' statement after the paper has
% been accepted, when creating the final version.  This will set the
% note in the first column to ``Proceedings of the...''
%\usepackage[accepted]{icml2016}
%-------------------------------------------------------------
%                      Own Commands
%-------------------------------------------------------------
\usepackage{amsmath}
\newcommand{\cbn}{\textsc{Cbn}}
\newcommand{\bn}{\textsc{Bn}}

\renewcommand{\algorithmiccomment}[1]{/* #1 */}
\def\ci{\perp\!\!\!\perp}
\def\dep{\perp\!\!\!\perp\!\!\!\!\!\!\!/\,\,\,\,}
% Theorem & Co environments and counters
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{equat}[theorem]{Equation}
\newtheorem{example}[theorem]{Example}
%-------------------------------------------------------------
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\etal}{\emph{et al.}}
\newcommand{\etc}{\emph{etc.}}
\newcommand{\cf}{\emph{cf.}}
\newcommand{\diff}[2]{\frac{\partial #1}{\partial #2}}
%\newcommand{\diff}[2]{\nabla_{#2}{#1}}
\newcommand{\vct}[1]{\ensuremath{\boldsymbol{#1}}} %for greek letters
\newcommand{\mat}[1]{\ensuremath{\mathbf{#1}}}
\newcommand{\set}[1]{\ensuremath{\mathcal{#1}}}
\newcommand{\con}[1]{\ensuremath{\mathsf{#1}}}
\newcommand{\T}{\ensuremath{\top}}
\newcommand{\mycomment}[1]{\textcolor{red}{#1}}
\newcommand{\ind}[1]{\ensuremath{\mathbbm 1_{#1}}}
\newcommand{\argmax}{\operatornamewithlimits{\arg\,\max}}
\newcommand{\erf}{\text{erf}}
\newcommand{\argmin}{\operatornamewithlimits{\arg\,\min}}
\newcommand{\bmat}[1]{\begin{bmatrix}#1\end{bmatrix}}
\newcommand{\mname}{\texttt{OLCS}}
\newcommand{\question}[1]{\textcolor{red}{Q: #1}}
\newcommand{\lrb}{\left{\right}}

@@

Give a training dataset $\set D = \left\{x_i\right\}_{i=1}^n$ with $x_i \in R^d$, \textit{i.i.d} drawn from certain distribution, we are interested at the predictive distribution of unknown target for the  test sample $x_*$, denoted as $f_*$. Suppose a prior over $\vct y$ given input $\vct X$ is a $n$-variable Gaussian distribution,
\[
\vct y \sim \set N(\vct 0, K(\vct X, \vct X))
\]
where $K(\vct X, \vct X)$ defines a covariance function over $\vct X$. Therefore the posterior of $f_*$ given the training dataset $\set D$ is also a Gaussian.
\[
f_*|\vct y, \vct X, x_* \sim \set N(\mu_*, \Sigma_*^{-1})
\]
where the sufficient statistics can be derived using Bayesian theorem,
\begin{align}
	& \mu_* = K_{X_*,X}\left[K_{X,X}+\sigma_n^2 I\right]^{-1}\vct y \label{eq:gpr_mu}\\
	& \Sigma_*^{-1} = K_{X_*,X_*} - K_{X_*,X}\left[K_{X,X}+\sigma_n^2 I\right]^{-1}K_{X,X_*} \label{eq:gpr_cov}
\end{align}
where $\sigma_n^2$ is the noise level and $K_{\cdot,\cdot}$ represents a shorthand for covariance matrix.
\question{Here comes the question of how to estimate the parameters for the covariance $K$.}

To obtain the Eq.\eqref{eq:gpr_mu}-\eqref{eq:gpr_cov}, we can use the following trick.
Given two variables $(\vct x, \vct y)$ following a Gaussian distribution,
\[
\bmat{\vct x\\ \vct y} \sim \set N\left(
\bmat{\mu_x \\ \mu_y}, \bmat{A & C \\ C^T & B}
\right)
\]
Then we have the conditional distribution,
\[
\vct x|\vct y \sim \set N\left(\mu_x+CB^{-1}(\vct y - \mu_y), A - C^TB^{-1}C \right)
\]

\section{PCA}
The basic idea of PCA is to maximally reduce information loss of projecting high dimensional data to lower dimension. Therefore, an intuitive consideration would be that we introduce first of all a projection matrix $\vct u$ on $d$-dimensional instance $x$, so that $x$ is mapped on a lower $m$-dimensional space. Following column vector routine, we expect that matrix $\vct u$ as being $m \times d$. Now given a dataset $ \vct X = \left\{  x_i\right\}_{i=1}^{n}$, it will be projected on a $ m $-dimensional space by $\vct u$. The objective of the projection is to maximize the covariance of data on the lower dimensional space, that is, 
\[
	\max \dfrac{1}{n}\sum_{i=1}^{n}\|\vct ux - \vct u\bar{x}\|^2 
\]
that can be rewritten as,
\begin{eqnarray}
	& \underset{\vct u}{\textit{maximize}}\quad \vct u S \vct u^T \nonumber \\ 
	\text{s.t.} & \vct u_i\vct u_i^T = 1, \,\, i=1,\ldots,m
	\label{eq:pca_obj}
\end{eqnarray}
where $S$ is the covariance of $\vct X$. To prevent $\vct u$ goes to infinity, we assume $\vct u$ has unit length, namely, $\vct u$ represents a set of basis of the lower dimension.

According to \eqref{eq:pca_obj}, we introduce $m$ Lagrangian multipliers $\vct \lambda$ as a diagonal matrix, and we have 
\[ L = \underset{\vct u}{\textit{maximize}}\quad \vct u S \vct u^T - \vct\lambda \vct u\vct u^T \]

Take the derivative of $L$ with respect to $\vct u$, we have
\begin{eqnarray}
	\vct uS & = & \vct\lambda\vct u \nonumber \\
	S & = & \vct u^{-1}\lambda\vct u
	\label{eq:pca_sol}
\end{eqnarray}
Since $\vct u$ is orthogonal, it is therefore not singular. We see that $\vct u$ and $\vct lambda$ are the indeed the eigenvectors and eigenvalues for $S$ respectively. And Eq.\eqref{eq:pca_sol} is exactly the singular value decomposition of $S=U\Sigma V^T$, we can derive $\vct u$ and $ \vct{\lambda} $ from $S$ conveniently.

\bibliography{myrefs}
\bibliographystyle{icml2016}
